visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2024-03-09 manuscript.tex
finalizing paper

Therefore, purpose of this manuscript is describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters. No known visualization techniques have been proposed for measurement invariance. By creating panel visualizations, we can supplement a researchers ability to judge the strength of the non-invariance differences and effect size for each item. The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance. Within this technique, the individual parameter effect sizes can calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups. Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful. This tutorial and package will help researchers plan future studies and aid in the ability to estimate a smallest effect of interest for measurement invariance studies, rather than relying on fit indices and rules of thumb alone.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial invariance, and create visualizations of parameters.
\item
  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
\item
  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
\item
  Understand the impact of measurement variability on replication and generalizability.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{complete}: The output from this model can be found in Figure \ref{fig:invariant-pic}. On the left hand side, the item invariance is plotted, and on the right hand side, the latent mean distributions for the two groups are plotted. In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals. Each visualization element was designed to match the traditional visualization for that type of output. All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate. All plots are made with \emph{ggplot2} and \emph{cowplot} (Wilke, 2020).
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  \texttt{intercept}: Only the left hand side of the complete plot designed to represent intercepts and factor loadings. Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)). The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four. The coefficient (\(b_1\)) for group 1 was 0.40, while the coefficient for group 2 was 0.21. The ribbon bands around the plotted slopes indicate the confidence interval for that estimate. In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\item
  \texttt{mean}: The right hand side of the complete plot graphing the latent variable means and density from the data. The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on. The lines indicate the means of the latent variables from the simulated dataset. Group labels are represented in the figure caption on the bottom. Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
\item
  \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item. Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\). It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate. Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot. The black bars represent the estimated residual for each group (group 1: 0.91, group 2: 1.22). The distributions are plotted to represent the normal spread of values using the standard error of the residuals. The violin plot allows for direct comparison of those residuals and their potential distributions. Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value. The plots are included separately so they can be arranged in a different fashion if desired.
\end{enumerate}

@@

The \(d_{MACS}\) value for item 4 in the invariant model was 0.16, representing a nil or unimportant difference in this manuscript. It is important to note that while Nye et al. (2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent. Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.53) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.68) differences. When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly). At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines. Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes. You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen et al., 2003). When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction. Here, we can use this same logic. If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.

@@

Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats. While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.19, and 0.16, respectively. These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation. At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference. The medium and large differences better illustrate differences in residuals across groups. Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation). The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter). The effect size difference of the residuals does not appear to change the effects in the latent means.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{boot.model.invariant }\OtherTok{\textless{}{-}} 
  \FunctionTok{bootstrap\_model}\NormalTok{(}
    \CommentTok{\# saved configural model }
    \AttributeTok{saved\_configural =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_configural,}
    \CommentTok{\# dataframe}
    \AttributeTok{data =}\NormalTok{ df.invariant,}
    \CommentTok{\# model syntax}
    \AttributeTok{model =}\NormalTok{ model.overall, }
    \CommentTok{\# group variable column in dataframe}
    \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
    \CommentTok{\# number of bootstraps}
    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
    \CommentTok{\# which fit index you would like to use}
    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
    \CommentTok{\# what is your criterion for that fit index}
    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{,}
    \CommentTok{\# what equality constraints are you testing }
    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"residuals"}\NormalTok{)}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{\# examine the loadings }
\NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## # A tibble: 0 x 4
## # i 4 variables: term <chr>, group <int>, estimate <dbl>, std.error <dbl>
\end{verbatim}

@@

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function. In general, we should expect \(M_{D}\) = 0.23 when items are invariant and \(M_{D}\) = 0.26 when items are not invariant. The effect size of non-invariant items ranges from 0.43 to 0.62.

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}
\caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample. The differences between intercepts are shown on the left hand side with a clear separation between lines. The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
\end{figure}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,598.681 & 7,661.900 & 0.946 & 0.893 & 0.078 & 0.035\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,820.090 & 3,872.912 & 0.969 & 0.938 & 0.067 & 0.034\\
Configural & 7,585.839 & 7,712.277 & 0.972 & 0.944 & 0.058 & 0.033\\
Loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
Intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
Residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,684.982 & 7,748.201 & 0.987 & 0.973 & 0.040 & 0.023\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,857.143 & 3,909.965 & 0.992 & 0.984 & 0.037 & 0.029\\
Configural & 7,622.892 & 7,749.330 & 0.986 & 0.972 & 0.042 & 0.030\\
Loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
Intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
Residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,382.013 & 7,445.232 & 0.997 & 0.995 & 0.016 & 0.018\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,602.905 & 3,655.727 & 1.000 & 1.013 & 0.000 & 0.023\\
Configural & 7,368.654 & 7,495.092 & 0.992 & 0.983 & 0.028 & 0.027\\
Loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
Intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
Residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,300.856 & 7,364.075 & 0.998 & 0.995 & 0.015 & 0.018\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,453.099 & 3,505.921 & 0.954 & 0.908 & 0.069 & 0.035\\
Configural & 7,218.848 & 7,345.287 & 0.965 & 0.929 & 0.059 & 0.033\\
Loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
Intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
Residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
lv =\textasciitilde{} q1 & 0.880 & 0.079\\
lv =\textasciitilde{} q2 & 0.898 & 0.074\\
lv =\textasciitilde{} q3 & 0.878 & 0.081\\
lv =\textasciitilde{} q4 & 0.962 & 0.045\\
lv =\textasciitilde{} q5 & 0.907 & 0.071\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
lv =\textasciitilde{} q1 & 0.762 & 0.116\\
lv =\textasciitilde{} q2 & 0.770 & 0.117\\
lv =\textasciitilde{} q3 & 0.762 & 0.119\\
lv =\textasciitilde{} q4 & 0.971 & 0.041\\
lv =\textasciitilde{} q5 & 0.842 & 0.097\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
q1 \textasciitilde{}\textasciitilde{} q1 & 0.869 & 0.075\\
q2 \textasciitilde{}\textasciitilde{} q2 & 0.860 & 0.078\\
q3 \textasciitilde{}\textasciitilde{} q3 & 0.870 & 0.075\\
q4 \textasciitilde{}\textasciitilde{} q4 & 0.994 & 0.016\\
q5 \textasciitilde{}\textasciitilde{} q5 & 0.862 & 0.077\\
lv \textasciitilde{}\textasciitilde{} lv & 0.864 & 0.075\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
q1 \textasciitilde{}\textasciitilde{} q1 & 0.558 & 0.140\\
q2 \textasciitilde{}\textasciitilde{} q2 & 0.559 & 0.140\\
q3 \textasciitilde{}\textasciitilde{} q3 & 0.560 & 0.140\\
q4 \textasciitilde{}\textasciitilde{} q4 & 0.972 & 0.035\\
q5 \textasciitilde{}\textasciitilde{} q5 & 0.559 & 0.140\\
lv \textasciitilde{}\textasciitilde{} lv & 0.562 & 0.137\\
\bottomrule
\end{tabular}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-1.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-2.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-3.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-4.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-5.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-6.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-7.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-103-8.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-110-1.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-111-1.pdf} \includegraphics{manuscript_files/figure-latex/unnamed-chunk-111-2.pdf}

>>>>

Therefore, purpose of this manuscript is to describe an \emph{R} package, \texttt{visualizemi}, that provides functionality to calculate multi-group confirmatory factor analysis, partial invariance tests, visualizations of the size of non-invariance, and potential effect sizes for overall models and individual parameters. No known visualization techniques have been proposed for measurement invariance. By creating panel visualizations, we can supplement a researcher's ability to judge the strength of the non-invariance differences and effect size for each item. The proposed effect sizes demonstrate the likelihood of replication with a similar sample as compared to a randomly assigned group model, thus, illustrating what type of measurement one might expect to find, and how different that is from random chance. Within this technique, the individual parameter effect sizes can be calculated: both the group differences within a model as compared to random and the likelihood of a parameter replication compared to random groups. Coupled with other indicators (i.e., fit indices differences, \(d_{MACS}\)), we can move toward a better understanding of how much measurement non-invariance is meaningful. This tutorial and package will help researchers plan future studies and aid in the ability to estimate a smallest effect of interest for measurement invariance studies, rather than relying on fit indices and rules of thumb alone.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Learn how to use \emph{visualizemi} to analyze multi-group confirmatory factor analysis, examine partial for invariance, and create visualizations of parameters.
\item
  Learn how to estimate the potential replication of multi-group models and their parameters using bootstrapping compared to a random group model.
\item
  Be able to calculate and interpret effect sizes for model and parameter replication, as well as parameter group differences.
\item
  Understand the impact of measurement variability on replication and generalizability.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{complete}: The output from this model can be found in Figure \ref{fig:invariant-pic}. On the left-hand side, the item invariance is plotted, and on the right-hand side, the latent mean distributions for the two groups are plotted. In the item invariance sub-plot, the visualization includes all three components traditionally seen in MGCFA testing steps: loadings, intercepts, and residuals. Each visualization element was designed to match the traditional visualization for that type of output. All parameter estimates are plotted on the unstandardized estimates and their confidence interval based on the standard error of the estimate. All plots are made with \emph{ggplot2} and \emph{cowplot} (Wilke, 2020).
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  \texttt{intercept}: Only the left-hand side of the complete plot designed to represent intercepts and factor loadings. Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable (\(\hat{Y} \sim b_0 + b_1X + \epsilon\)). The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four. The coefficient (\(b_1\)) for group 1 was 0.40, while the coefficient for group 2 was 0.21. The ribbon bands around the plotted slopes indicate the confidence interval for that estimate. In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\item
  \texttt{mean}: The right-hand side of the complete plot graphing the latent variable means and density from the data. The latent variable is shown on the x-axis using standardized values (i.e., \emph{z}-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on. The lines indicate the means of the latent variables from the simulated dataset. Group labels are represented in the figure caption on the bottom. Group 1 is usually the group that is alphabetically first in the data set or whichever group is the first that appears when using the \texttt{levels()} command.
\item
  \texttt{variance}: A split geom violin plot indicating the variance distribution of the plotted item. Residuals are trickier to plot, as they are the left over error when predicting the observed variables \(\epsilon\). It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate. Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot. The black bars represent the estimated residual for each group (group 1: 0.91, group 2: 1.22). The distributions are plotted to represent the normal spread of values using the standard error of the residuals. The violin plot allows for direct comparison of those residuals and their potential distributions. Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value. The plots are included separately so they can be arranged in a different fashion if desired.
\end{enumerate}

@@

The \(d_{MACS}\) value for item 4 in the invariant model was 0.16, representing a nil or unimportant difference in this manuscript. It is important to note that while Nye et al. (2019) suggests specific sizes for small, medium, and large, each researcher should determine for themselves what effects represent. Figure \ref{fig:small-load-pic} displays the results from the small (\(d_{MACS}\) = 0.27) difference in loadings, while Figure \ref{fig:med-load-pic} displays the results from the medium (\(d_{MACS}\) = 0.61) difference in loadings, and Figure \ref{fig:large-load-pic} shows the large (\(d_{MACS}\) = 0.66) differences. When investigating the slope values, we can clearly see the change in the loading for the second group (the only manipulated variable, although random data set generation may also change intercepts and residuals slightly). At the medium effect size, we see that the confidence bands do not overlap (at the edges), and at the large effect size, we can see a clear separation of two lines. Note that the intercepts in this model are estimated as equal so the loading representation will not literally separate, but the steepness of the lines is the indicator of the difference between the slopes. You can imagine these lines are interpreted like a simple slopes analysis for interactions in regression (Cohen et al., 2003). When simple slopes for interactions are plotted, if they are parallel, there is no interaction, and if they cross, then there is an interaction. Here, we can use this same logic. If they are parallel, there is likely invariance (they are the same), and the further from parallel they become, the larger the effect size for the differences between group loadings.

@@

Last, the effect of the residuals is plotted in small (Figure \ref{fig:small-res-pic}), medium (Figure \ref{fig:med-res-pic}), and large (Figure \ref{fig:large-res-pic}) formats. While \(d_{MACS}\) values are not technically available for the residuals, our models showed 0.19, 0.10, and 0.16, respectively. These differences in values are variable due to the random generation of data sets for each measurement invariance manipulation. At first glance, the differences in the small chart may seem large, because the black lines are not touching, but notice that the distributions overlap, indicating a likely small difference. The medium and large differences better illustrate differences in residuals across groups. Further, the impact of the residuals on the shape of the latent mean distribution can also been seen (and unintentionally, in the first figures as well due to random variation). The impact is due to the standard error of the residuals, as smaller standard errors represent lepokurtic distributions (taller), and larger standard errors represent platykurtic distributions (flatter). The effect size difference of the residuals does not appear to change the effects in the latent means.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{boot.model.invariant }\OtherTok{\textless{}{-}} 
  \FunctionTok{bootstrap\_model}\NormalTok{(}
    \CommentTok{\# saved configural model }
    \AttributeTok{saved\_configural =}\NormalTok{ results.invariant}\SpecialCharTok{$}\NormalTok{model\_configural,}
    \CommentTok{\# dataframe}
    \AttributeTok{data =}\NormalTok{ df.invariant,}
    \CommentTok{\# model syntax}
    \AttributeTok{model =}\NormalTok{ model.overall, }
    \CommentTok{\# group variable column in dataframe}
    \AttributeTok{group =} \StringTok{"group"}\NormalTok{,}
    \CommentTok{\# number of bootstraps}
    \AttributeTok{nboot =} \DecValTok{1000}\NormalTok{, }
    \CommentTok{\# which fit index you would like to use}
    \AttributeTok{invariance\_index =} \StringTok{"cfi"}\NormalTok{,}
    \CommentTok{\# what is your criterion for that fit index}
    \AttributeTok{invariance\_rule =}\NormalTok{ .}\DecValTok{01}\NormalTok{,}
    \CommentTok{\# what equality constraints are you testing }
    \AttributeTok{group.equal =} \FunctionTok{c}\NormalTok{(}\StringTok{"loadings"}\NormalTok{, }\StringTok{"intercepts"}\NormalTok{, }\StringTok{"resduals"}\NormalTok{)}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{\# examine the loadings }
\NormalTok{partial.rs}\FloatTok{.2}\SpecialCharTok{$}\NormalTok{model\_coef }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(term }\SpecialCharTok{==} \StringTok{"RS6 \textasciitilde{}1 "}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(model }\SpecialCharTok{==} \StringTok{"intercepts"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
\NormalTok{  dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(term, group, estimate, std.error)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## # A tibble: 2 x 4
##   term      group estimate std.error
##   <chr>     <int>    <dbl>     <dbl>
## 1 "RS6 ~1 "     1     5.00    0.0605
## 2 "RS6 ~1 "     2     4.54    0.0533
\end{verbatim}

@@

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function. In general, we should expect \(M_{D}\) = 0.11 when items are invariant and \(M_{D}\) = 0.25 when items are not invariant. The effect size of non-invariant items ranges from 0.43 to 0.59.

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs14-chinese-pic-1.pdf}
\caption{\label{fig:rs14-chinese-pic}The differences in intercepts for the second item on the RS14 by language sample. The differences between intercepts are shown on the left-hand side with a clear separation between lines. The latent means also show a clear difference between groups where the English group appears to have lower scores overall than the Chinese group.}
\end{figure}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,595.822 & 7,659.041 & 1.000 & 1.017 & 0.000 & 0.012\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,815.314 & 3,868.136 & 0.996 & 0.991 & 0.025 & 0.023\\
Configural & 7,581.063 & 7,707.501 & 0.988 & 0.976 & 0.038 & 0.027\\
Loadings & 7,609.348 & 7,718.928 & 0.878 & 0.826 & 0.101 & 0.079\\
Intercepts & 7,601.550 & 7,694.271 & 0.891 & 0.879 & 0.084 & 0.079\\
Residuals & 7,596.811 & 7,668.459 & 0.890 & 0.905 & 0.075 & 0.096\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,665.760 & 7,728.979 & 1.000 & 1.022 & 0.000 & 0.010\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,855.953 & 3,908.775 & 0.997 & 0.995 & 0.020 & 0.023\\
Configural & 7,621.702 & 7,748.140 & 0.989 & 0.978 & 0.036 & 0.027\\
Loadings & 7,659.690 & 7,769.270 & 0.852 & 0.789 & 0.114 & 0.088\\
Intercepts & 7,652.360 & 7,745.081 & 0.863 & 0.848 & 0.097 & 0.088\\
Residuals & 7,664.853 & 7,736.502 & 0.806 & 0.832 & 0.102 & 0.135\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,382.876 & 7,446.095 & 0.992 & 0.985 & 0.028 & 0.020\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,601.920 & 3,654.742 & 1.000 & 1.023 & 0.000 & 0.018\\
Configural & 7,367.669 & 7,494.108 & 0.996 & 0.992 & 0.020 & 0.025\\
Loadings & 7,371.027 & 7,480.607 & 0.969 & 0.956 & 0.049 & 0.046\\
Intercepts & 7,364.724 & 7,457.446 & 0.977 & 0.975 & 0.037 & 0.047\\
Residuals & 7,386.854 & 7,458.502 & 0.877 & 0.893 & 0.076 & 0.076\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,301.897 & 7,365.116 & 0.993 & 0.986 & 0.026 & 0.019\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,454.309 & 3,507.131 & 0.945 & 0.889 & 0.075 & 0.036\\
Configural & 7,220.058 & 7,346.496 & 0.960 & 0.920 & 0.063 & 0.034\\
Loadings & 7,218.878 & 7,328.458 & 0.948 & 0.926 & 0.060 & 0.046\\
Intercepts & 7,213.011 & 7,305.732 & 0.956 & 0.951 & 0.049 & 0.048\\
Residuals & 7,305.660 & 7,377.309 & 0.559 & 0.617 & 0.137 & 0.189\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
lv =\textasciitilde{} q1 & 0.890 & 0.075\\
lv =\textasciitilde{} q2 & 0.904 & 0.072\\
lv =\textasciitilde{} q3 & 0.887 & 0.078\\
lv =\textasciitilde{} q4 & 1.000 & 0.000\\
lv =\textasciitilde{} q5 & 0.914 & 0.068\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
lv =\textasciitilde{} q1 & 0.806 & 0.102\\
lv =\textasciitilde{} q2 & 0.812 & 0.102\\
lv =\textasciitilde{} q3 & 0.813 & 0.102\\
lv =\textasciitilde{} q4 & 1.000 & 0.000\\
lv =\textasciitilde{} q5 & 0.861 & 0.088\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
q1 \textasciitilde{}\textasciitilde{} q1 & 0.879 & 0.077\\
q2 \textasciitilde{}\textasciitilde{} q2 & 0.873 & 0.079\\
q3 \textasciitilde{}\textasciitilde{} q3 & 0.878 & 0.077\\
q4 \textasciitilde{}\textasciitilde{} q4 & 0.980 & 0.031\\
q5 \textasciitilde{}\textasciitilde{} q5 & 0.873 & 0.079\\
lv \textasciitilde{}\textasciitilde{} lv & 0.877 & 0.076\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
Estimated Parameter & CFI & RSMEA\\
\midrule
q1 \textasciitilde{}\textasciitilde{} q1 & 0.555 & 0.141\\
q2 \textasciitilde{}\textasciitilde{} q2 & 0.556 & 0.141\\
q3 \textasciitilde{}\textasciitilde{} q3 & 0.556 & 0.141\\
q4 \textasciitilde{}\textasciitilde{} q4 & 0.967 & 0.039\\
q5 \textasciitilde{}\textasciitilde{} q5 & 0.557 & 0.141\\
lv \textasciitilde{}\textasciitilde{} lv & 0.559 & 0.137\\
\bottomrule
\end{tabular}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-1.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-2.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-3.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-4.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-5.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-6.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-7.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-107-8.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-114-1.pdf}

@@

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-115-1.pdf} \includegraphics{manuscript_files/figure-latex/unnamed-chunk-115-2.pdf}
